Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-26 snapshot_system/arch.tex
modify all sections

As  depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication component,
3) an append store client which provides facilities to store  and access snapshot data,
and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
in Section~\ref{sec:dedup}.

@@

\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation
%\subsection{Inner and corss VM deduplication}
Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independence between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

@@

@@

For example, letting $P_1 = 0.01$ and $t=1.0$, 
we would expect deletion phase-2 be triggered once for 
every $T/P_{bl} = 100$ runs of deletion phase-1.
On a node that hosts 20 VMs and each VM deletes one snapshot per day, there would be 
only 1 deletion phase-2 scheduled for every 5 days, which is sufficiently small to prevent the 
heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.

>>>>

As  depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication component,
3) an append store client to store  and access snapshot data,
and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
in Section~\ref{sec:dedup}.

@@

\comments{
\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation
%\subsection{Inner and corss VM deduplication}
Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independence between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

@@

\comments{

@@

For example, letting $P_1 = 0.01$ and $t=1.0$, 
we would expect deletion phase-2 be triggered once for 
every $T/P_{bl} = 100$ runs of deletion phase-1.
On a node that hosts 20 VMs and each VM deletes one snapshot per day, there would be 
only 1 deletion phase-2 scheduled for every 5 days, which is sufficiently small to prevent the 
heavy I/O workload of deletion phase-2 from disturbing normal VM opeations.
}
